---
title: "Research vision"
output: html_document
---
<!--- Aim: To show the shape of the central question -->
<!--- Set up --->
```{r set-up, include=FALSE}
library(here)
library(dplyr)
library(readr)
library(tidyr)
library(tibble)
library(purrr)
library(ggplot2)
library(patchwork)
library(kableExtra)
theme_set(theme_classic())
knitr::opts_chunk$set(
  eval = TRUE, echo = FALSE,
  message = FALSE, warning = FALSE
)
```

```{r data}
# Simulate data with a quadratic relationship and random x-values
set.seed(123)
qt <- 1:10
ql <- c(5,6,7,8,9,10,9,8,7,6)
q2 <- qt^2

qt2values <- seq(0, 10, 0.1)
quadratic.model <-lm(ql ~ qt + q2)
predictedql <- predict(quadratic.model, list(qt=qt, q2=qt2values^2))
plot(qt, ql)
lines(qtvalues, predictedql, col = "darkgreen", lwd = 3)
```

role of quantifying expert advice under pressure: high uncertainty, time-critical decision-making
- time constrained
- limited data
- models no substitute for data; suggest what data to collect

We should be clear about the cost-effectiveness of additional investment in modelling effort
Ensemble performance reflects a bias-variance trade-off
We can adopt the concept of "effective sample size" - 
